Dewlap color variation in \textit{Anolis sagrei} is maintained among habitats within islands of the West Indies

### 2021-05-29 ms/sections/figures.tex
added Colin's figure

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=\textwidth]{figures/Figure1_CMD-01_cropped.png}
	\caption{Overview of our study design, including a map of the Bahamas and the Cayman Islands, on which are indicated the nine islands we sampled, two representatives of our study species \textit{Anolis sagrei} with their dewlaps deployed, and the three types of habitats we considered on each island.}
	\label{fig:overview}
\end{figure}
